### 2009-09-08 doc/tech_doc/xrsl/xrsl-urls.tex
add new URL option tcpnodelay; correct checksum options

\begin{tabular}{lp{10cm}}
   \verb#threads=<number># & specifies number of parallel
   streams to be used by GridFTP or HTTP(s,g); default value is 1,
   maximal value is 10\\
   \verb#cache=yes|no|renew|copy# & indicates whether the GM should
   cache the file; default for input files is \verb#yes#. \verb#renew#
   forces a download of the file, even if the cached copy is still valid.
   \verb#copy# forces the cached file to be copied (rather than linked) to
   the session dir, this is useful if for example the file is to be modified.\\
   \verb#readonly=yes|no# & for transfers to \verb#file://# destinations,
   specifies whether the file should be
   read-only (unmodifiable) or not; default is \verb#yes# \\
   \verb#secure=yes|no# & indicates whether the GridFTP data
   channel should be encrypted; default is \verb#no#\\
   \verb#blocksize=<number># & specifies size of
   chunks/blocks/buffers used in GridFTP or HTTP(s,g) transactions;
   default is protocol dependent\\ 
   \verb#checksum=cksum|md5|adler32# & specifies the algorithm for checksum to be
   computed (ev. provided to the indexing server). This is overridden
   by any metadata options specified (see below). If this option is
   not provided, the default for the protocol is used. \verb#checksum=no#
   in a source URL will disable checksum verification.\\ 
   \verb#exec=yes|no# & means the file should be treated as executable\\
   \verb#preserve=yes|no# & specify if file must be uploaded to this
   destination even if job processing failed (default is \verb#no#)\\
   \verb#pattern=<pattern># & defines file matching pattern; currently
   works for file listing requests sent to an \verb#se://# endpoint\\
   \verb#guid=yes|no# & make software use GUIDs instead of LFNs while
   communicating to indexing services; meaningful for \verb#rls://#
   only\\
   \verb#overwrite=yes|no# & make software try to overwrite existing
   file(s), i.e. before writing to destination, tools will try to remove
   any information/content associated with specified URL\\
   \verb#protocol=gsi|gssapi# & to distinguish between two kinds of 
   \verb#httpg#. \verb#gssapi# stands for implemention using only GSSAPI 
   functions to wrap data and \verb#gsi# uses additional headers as 
   implmented in Globus IO\\
   \verb#spacetoken=<pattern># & specify the space token to be used for
   uploads to SRM storage elements supporting SRM version 2.2 or higher\\
   \verb#autodir=yes|no# & specify if before writing to specified location
   software should try to create all directories mentioned in specified
   URL. Currently this applies to FTP and GridFTP only. Default for those
   protocols is \verb#yes#\\
\end{tabular}

@@

\begin{tabular}{lp{10cm}}
   \verb#guid# & GUID of the file in the metadata service \\
   \verb#checksumtype# & Type of checksum. Supported values are cksum
   (default), md5 and ad (adler32 checksum) \\
   \verb#checksumvalue# & The checksum of the file \\
\end{tabular}

@@

\begin{framed}
   Examples of URLs are:\\
   \\
   \verb#http://grid.domain.org/dir/script.sh#\\
   \verb#gsiftp://grid.domain.org:2811;threads=10;secure=yes/dir/input_12378.dat#\\
   \verb#ldap://grid.domain.org:389/lc=collection1,rc=Nordugrid,dc=nordugrid,dc=org#\\
   \verb#rc://grid.domain.org/lc=collection1,rc=Nordugrid,dc=nordugrid,dc=org/zebra/f1.zebra#\\
   \verb#rls://gsiftp://se.domain.org/datapath/file25.dat@grid.domain.org:61238/myfile02.dat#$^1$\\
   \verb#fireman://fireman_host:8443/glite-data-catalog-interface/FiremanCatalog?data.root#\\
   \verb#file:///home/auser/griddir/steer.cra#\\
   \verb#lfc://srm://srm.domain.org/griddir@lfc.domain.org//user/file1:guid=\# \\
   \verb#    bc68cdd0-bf94-41ce-ab5a-06a1512764dc:checksumtype=ad:checksumvalue=12345678#$^2$\\
   \verb#lfc://;cache=no@lfc.domain.org/:guid=bc68cdd0-bf94-41ce-ab5a-06a1512764d#$^3$\\
\end{framed}

>>>>

\begin{tabular}{lp{10cm}}
   \verb#threads=<number># & specifies number of parallel
   streams to be used by GridFTP or HTTP(s,g); default value is 1,
   maximal value is 10\\
   \verb#cache=yes|no|renew|copy# & indicates whether the GM should
   cache the file; default for input files is \verb#yes#. \verb#renew#
   forces a download of the file, even if the cached copy is still valid.
   \verb#copy# forces the cached file to be copied (rather than linked) to
   the session dir, this is useful if for example the file is to be modified.\\
   \verb#readonly=yes|no# & for transfers to \verb#file://# destinations,
   specifies whether the file should be
   read-only (unmodifiable) or not; default is \verb#yes# \\
   \verb#secure=yes|no# & indicates whether the GridFTP data
   channel should be encrypted; default is \verb#no#\\
   \verb#blocksize=<number># & specifies size of
   chunks/blocks/buffers used in GridFTP or HTTP(s,g) transactions;
   default is protocol dependent\\ 
   \verb#checksum=cksum|md5|adler32# & specifies the algorithm for checksum to be
   computed (ev. provided to the indexing server). This is overridden
   by any metadata options specified (see below).\\ 
   \verb#exec=yes|no# & means the file should be treated as executable\\
   \verb#preserve=yes|no# & specify if file must be uploaded to this
   destination even if job processing failed (default is \verb#no#)\\
   \verb#pattern=<pattern># & defines file matching pattern; currently
   works for file listing requests sent to an \verb#se://# endpoint\\
   \verb#guid=yes|no# & make software use GUIDs instead of LFNs while
   communicating to indexing services; meaningful for \verb#rls://#
   only\\
   \verb#overwrite=yes|no# & make software try to overwrite existing
   file(s), i.e. before writing to destination, tools will try to remove
   any information/content associated with specified URL\\
   \verb#protocol=gsi|gssapi# & to distinguish between two kinds of 
   \verb#httpg#. \verb#gssapi# stands for implemention using only GSSAPI 
   functions to wrap data and \verb#gsi# uses additional headers as 
   implmented in Globus IO\\
   \verb#spacetoken=<pattern># & specify the space token to be used for
   uploads to SRM storage elements supporting SRM version 2.2 or higher\\
   \verb#autodir=yes|no# & specify if before writing to specified location
   software should try to create all directories mentioned in specified
   URL. Currently this applies to FTP and GridFTP only. Default for those
   protocols is \verb#yes#\\
   \verb#tcpnodelay=yes|no# & controls the use of the TCP\_NODELAY
   socket option (which disables the Nagle algorithm). Applies to
   http(s) only. Default is \verb#no#\\ 
\end{tabular}

@@

\begin{tabular}{lp{10cm}}
   \verb#guid# & GUID of the file in the metadata service \\
   \verb#checksumtype# & Type of checksum. Supported values are cksum
   (default), md5 and adler32 \\
   \verb#checksumvalue# & The checksum of the file \\
\end{tabular}

@@

\begin{framed}
   Examples of URLs are:\\
   \\
   \verb#http://grid.domain.org/dir/script.sh#\\
   \verb#gsiftp://grid.domain.org:2811;threads=10;secure=yes/dir/input_12378.dat#\\
   \verb#ldap://grid.domain.org:389/lc=collection1,rc=Nordugrid,dc=nordugrid,dc=org#\\
   \verb#rc://grid.domain.org/lc=collection1,rc=Nordugrid,dc=nordugrid,dc=org/zebra/f1.zebra#\\
   \verb#rls://gsiftp://se.domain.org/datapath/file25.dat@grid.domain.org:61238/myfile02.dat#$^1$\\
   \verb#fireman://fireman_host:8443/glite-data-catalog-interface/FiremanCatalog?data.root#\\
   \verb#file:///home/auser/griddir/steer.cra#\\
   \verb#lfc://srm://srm.domain.org/griddir@lfc.domain.org//user/file1:guid=\# \\
   \verb#    bc68cdd0-bf94-41ce-ab5a-06a1512764dc:checksumtype=adler32:checksumvalue=12345678#$^2$\\
   \verb#lfc://;cache=no@lfc.domain.org/:guid=bc68cdd0-bf94-41ce-ab5a-06a1512764d#$^3$\\
\end{framed}
